Towards Detecting Stalkerware Through Network Traces

### 2019-03-22 paper/main.tex
Intro

\section{Introduction}
One in four women and one in six men will be subject to some sort of intimate 
partner abuse during their lifetimes, where ``intimate partner abuse'' can 
include physical, emotional, or sexual abuse, as well as stalking or rape. In a 
world where technology now pervades every aspect of our lives, some 
aspects of IPV have recently changed too. Specifically, there are more options 
available to the abuser for attempting to retain control over their partner. 
One of these options is the ability to install monitoring software on their 
partner's phone or computer to record their online activity, communications, 
and location. We refer to such software as ``stalkerware.''

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.5\columnwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{../images/CellPhoneTracker.png}
		\caption{SpyToMobile's setup page }
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{0.5\columnwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{../images/CoupleTrackerSetup.png}
		\caption{One of the setup pages for Couple}
		\label{fig:sub2}
	\end{subfigure}
	\caption{SpyToMobile and Couple's similarities. All SpyToMobile copies have 
	the same setup screen as \ref{fig:sub1} as well as identical signatures. 
	Couple did not share signatures with SpyToMobile.}
	\label{fig:spytomobile_couple}
\end{figure}

@@

	Texting, Chat, Phone Spy by Maxlo & Domain:spy2mobile.com & SpyToMobile lookalike \\
\end{tabular}

\section{Wireshark Display Filters for Specific Signatures}
\begin{lstlisting}
ip.host contains dedicated.codero.net 
|| http.host contains hellospy
|| (ip.host contains data-api.spymyfone.com && ssl.handshake.extension.data 
contains "my.spymyfone.com") 
|| (ip.host contains ws.spyzie.com && ssl.handshake.extension.data contains 
"ws.spyzie.com") 
|| ip.host contains data-api.spymyfone.com 
|| ip.host contains ws.spyzie.com 
|| ip.host contains phonedata.me 
|| ssl.handshake.extension.data contains "phonedata.me" 
|| ip.host contains apiv4.alter757.info 
|| ssl.handshake.extension.data contains "thd.cc" 
|| ip.host contains thd.cc 
|| ip.host contains mspyonline.com 
|| ip.host contains corexchange.com && ssl.handshake.extensions_server_name 
contains messages02.smstracker.com 
|| ip.host contains life360.helpshift.com 
|| ip.host contains antitheft.ns1.ff.avast.com 
|| (ip.host contains production-finderapps && 
ssl.handshake.extensions_server_name contains "api.familysafetyproduction.com") 
|| ip.host contains production-finderapps 
|| ssl.handshake.extensions_server_name contains "celulocen.zendesk.com" 
|| ip.host contains www.zoemob.com 
|| ip.host contains unifiedlayer.com 
|| http.host matches "callsmstracker" 
|| ip.dst_host matches "onlinehome-server" 
|| (ip.dst_host matches "spoc-mu(|w|e)1.norton" && http.user_agent matches 
"(android|ios)")
|| ssl.handshake.extensions_server_name matches "family.norton" 
|| (udp && ip.host contains stun.l.google.com) 
|| http.host == relay.google.com && http.user_agent matches test 
|| http.host matches "97.logger.mobi" 
|| ssl.handshake.extensions_server_name matches "gpswox" 
|| ip.dst_host matches "gpswox" 
|| ssl.handshake.extensions_server_name matches "geozilla" 
|| ip.dst_host matches "clients.your-server.de" 
|| (ip.addr == 66.147.232.135 && tcp.port == 8080 && http.request.uri contains 
"signalr") 
|| ip.addr == 66.147.232.135 && tcp.port == 8080 
|| ssl.handshake.extensions_server_name matches "findmykids" 
|| ssl.handshake.extension.data contains "findmykids"  
||  ip.dst_host matches "(trackmyphones.com)" 
|| http.host matches "callsmstracker" 
|| ip.dst_host matches "onlinehome-server" 
\end{lstlisting}

\section{General Signature Wireshark Display Filters}

>>>>

\section{Introduction}
Intimate partner violence, or IPV, is a pervasive problem in the United States 
and elsewhere. One in four women and one in six men will be subject to some 
sort of intimate 
partner abuse during their lifetimes, where ``intimate partner abuse'' can 
include physical, emotional, or sexual abuse, as well as stalking or rape. In a 
world where technology now pervades every aspect of our lives, some 
aspects of IPV have changed too. Technology can now be abused in a variety of 
ways that harm survivors of IPV. Previous work \cite{ristenpart_ucsd_talk} has 
classified these into four categories of attacks: ownership-based, account or 
device compromise, harmful messages or posts, and exposure of private 
information. Ownership-based attacks are possible when the abuser owns the 
device used by the victim or the victim's children. They are then capable 
of installing software on it that can remotely destroy the device or prevent or 
monitor access and usage. Attacks based on account or device compromise are 
possible when the abuser does not own the device but nevertheless can guess 
passwords or compel the victim to reveal them, or has access to the unlocked 
device, or can remotely ``hack'' it using knowledge of security questions or 
passwords. Some examples of a ``harmful message'' attack include messaging the 
victim from a spoofed account, messaging the victim's family or friends, or 
impersonating the victim using their own accounts. Finally, attacks that expose 
private information can involve ``revenge pornography,'' revealing an HIV 
status, creating fake profiles offering sexual services, and blackmail. While 
some of these options (such as tracking a victim's location) are available to 
an abuser without installing any extra software on the phone, others are not. 
We refer to monitoring software that can record online activity, 
communications, and location, or remotely tamper with the device, as 
``stalkerware.''

@@

\begin{figure}
	\centering
	\begin{subfigure}{0.5\columnwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{../images/CellPhoneTracker.png}
		\caption{SpyToMobile's setup page }
		\label{fig:sub1}
	\end{subfigure}%
	\begin{subfigure}{0.5\columnwidth}
		\centering
		\includegraphics[width=0.9\linewidth]{../images/Couple_like_spy2mobile.png}
		\caption{A setup page for Couple}
		\label{fig:sub2}
	\end{subfigure}
	\caption{SpyToMobile and Couple's similarities. All SpyToMobile copies have 
	the same setup screen as \ref{fig:sub1} as well as identical signatures. 
	Couple did not share signatures with SpyToMobile.}
	\label{fig:spytomobile_couple}
\end{figure}

@@

	Texting, Chat, Phone Spy by Maxlo & Domain:spy2mobile.com & SpyToMobile lookalike \\
\end{tabular}
\end{table*}

\section{Wireshark Display Filters for Specific Signatures}
\begin{lstlisting}
ip.host contains dedicated.codero.net 
|| http.host contains hellospy
|| (ip.host contains data-api.spymyfone.com && ssl.handshake.extension.data 
contains "my.spymyfone.com") 
|| (ip.host contains ws.spyzie.com && ssl.handshake.extension.data contains 
"ws.spyzie.com") 
|| ip.host contains data-api.spymyfone.com 
|| ip.host contains ws.spyzie.com 
|| ip.host contains phonedata.me 
|| ssl.handshake.extension.data contains "phonedata.me" 
|| ip.host contains apiv4.alter757.info 
|| ssl.handshake.extension.data contains "thd.cc" 
|| ip.host contains thd.cc 
|| ip.host contains mspyonline.com 
|| ip.host contains corexchange.com && ssl.handshake.extensions_server_name 
contains messages02.smstracker.com 
|| ip.host contains life360.helpshift.com 
|| ip.host contains antitheft.ns1.ff.avast.com 
|| (ip.host contains production-finderapps && 
ssl.handshake.extensions_server_name contains "api.familysafetyproduction.com") 
|| ip.host contains production-finderapps 
|| ssl.handshake.extensions_server_name contains "celulocen.zendesk.com" 
|| ip.host contains www.zoemob.com 
|| ip.host contains unifiedlayer.com 
|| http.host matches "callsmstracker" 
|| ip.dst_host matches "onlinehome-server" 
|| (ip.dst_host matches "spoc-mu(|w|e)1.norton" && http.user_agent matches 
"(android|ios)")
|| ssl.handshake.extensions_server_name matches "family.norton" 
|| (udp && ip.host contains stun.l.google.com) 
|| http.host == relay.google.com && http.user_agent matches test 
|| http.host matches "97.logger.mobi" 
|| ssl.handshake.extensions_server_name matches "gpswox" 
|| ip.dst_host matches "gpswox" 
|| ssl.handshake.extensions_server_name matches "geozilla" 
|| ip.dst_host matches "clients.your-server.de" 
|| (ip.addr == 66.147.232.135 && tcp.port == 8080 && http.request.uri contains 
"signalr") 
|| ip.addr == 66.147.232.135 && tcp.port == 8080 
|| ssl.handshake.extensions_server_name matches "findmykids" 
|| ssl.handshake.extension.data contains "findmykids"  
||  ip.dst_host matches "(trackmyphones.com)" 
|| http.host matches "callsmstracker" 
|| ip.dst_host matches "onlinehome-server" 
\end{lstlisting}
\section{General Signature Wireshark Display Filters}
